### 2021-10-13 chapters/introduction.tex
Changes due to examination comments continued

    Finally, simulations of the remnant are dependent on the spatial resolution.
    Generally, increasing the spatial resolution leads to more accurate simulations at the cost of simulation time.
    Ref.~\cite{Dietrich2018} state that their post-merger simulations from  the \texttt{CoRe} database are accurate enough to infer the energy and frequency content of the post-merger remnant.
    This is an important point: the uncertainty in the phase evolution  and collapse time of the post-merger remnant, which is discussed further in Sec.~\ref{sec:Intro:StrainAndSpectra}, has had a significant impact on the design of the models developed in this thesis.

>>>>

    Finally, simulations of the remnant are dependent on the spatial resolution.
    Generally, increasing the spatial resolution leads to more accurate simulations at the cost of simulation time.
    Ref.~\cite{Dietrich2018} state that their post-merger simulations from  the \texttt{CoRe} database are accurate enough to infer the energy and frequency content of the post-merger remnant.
    \redtext{Additionally, a recent examination of waveform systematics found that existing waveform models, including numerical-relativity simulations, were not accurate enough to inform the equation of state at very loud SNRs ($\gtrsim 100$) expected from third-generation detectors~\cite{Gamba2021}.
    These are important points: the uncertainty in the phase evolution  and collapse time of the post-merger remnant, which is discussed further in Sec.~\ref{sec:Intro:StrainAndSpectra}, has had a significant impact on the design of the models developed in this thesis.}
